Dynamics of innovation in stigmergic collectives

### 2023-05-10 LaTeX/draft.tex
EpsilonGreedyWorking

\subsection*{Single agent learning}

>>>>

\subsection*{Single agent learning}
Now that we have the environment and the agent behavior laid out, we look at the learning dynamics of the agent
when it has no feedback through pheromone but still tries to perform the distance-accuracy tradeoff. The agent can
make this tradeoff by exploring the environment as well as exploiting its intrinsic ability to follow pheromone to
accumulate reward. This is established through an $\epsilon$-greedy policy and we look at the evolution of the value
function as the agent so learns by following this strategy.

Mention that the TD(0)-learning results in
\[
    v(s_c) \leftarrow (1-\alpha) v(s_c) + \alpha r(s^*)
\]
as $v(s^*) = 0$.
